Synthesising Complex Termination Arguments

### 2014-05-30 papers/termination/paper.tex
Added skeleton results tables

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{pifont}

@@

\section{Experiments}

\begin{figure*}
\centering
\begin{tabular}{|l|l|l||l|l|l|l|}
\hline
    & LOC & Rank function size & \textsc{T2} & \textsc{ARMC} & \textsc{Headshot} & \textsc{Headshot-Linear} \\
    \hline
    \hline
 P1 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P2 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 P3 & 10 & 3 & 100s & 70s & 0.1s & \bf{0.01s} \\
 \hline
\end{tabular}
\caption{Termination for linear programs with disjunctive, linear ranking functions\label{fig:linear}}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
    & LOC & Ranking program size & Lexicarity & Linear program? & Linear ranking function? & Time (s)\\
    \hline
    \hline
 P1 & 10 & 3 & 1 & \xmark & \xmark & 0.01 \\
 P2 & 10 & 3 & 1 & \xmark & \xmark & 0.01 \\
 P3 & 10 & 3 & 1 & \xmark & \xmark & 0.01 \\
 \hline
\end{tabular}

\caption{\textsc{Headshot} termination for nonlinear programs with nonlinear ranking functions\label{fig:nonlinear}}
 \end{figure*}
